---
title: "Regression Model Project"
author: "Aruna"
date: "5/31/2020"
output: pdf_document
---
## Overview 
In the project we will work on Motor Trend, a magazine about the automobile industry. Looking at a data set of a collection of cars, and exploring the relationship between a set of variables and miles per gallon (MPG) (outcome). We are particularly interested in the following two questions:

1. Is an automatic or manual transmission better for MPG
2. Quantify the MPG difference between automatic and manual transmissions

Using simple linear regression analysis, we determine that there is a signficant difference between the mean MPG for automatic and manual transmission cars. 


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
data(mtcars)
mtcars$vs <- factor(mtcars$vs)
mtcars$am.label <- factor(mtcars$am, labels=c("Automatic","Manual")) # 0=automatic, 1=manual
mtcars$gear <- factor(mtcars$gear)
mtcars$carb <- factor(mtcars$carb)
head(mtcars)
boxplot(mpg ~ am.label, data = mtcars, col = (c("red","blue")), ylab = "Miles Per Gallon", xlab = "Transmission Type")
```
We can that Manual Transmission provides better MPG

## Regression Analysis
Now calculate mean MPG values for cars with Automatic and Manual transmission
```{r}
aggregate(mtcars$mpg,by=list(mtcars$am.label),FUN=mean)
```
We can see again that Manual transmission yields on average 7 MPG more than Automatic

### Simple Linear Regression Test
```{r}
T_simple <- lm(mpg ~ factor(am), data=mtcars)
summary(T_simple)
```
The p-value is less than 0.003, so we will not reject the hypothesis. 

Let’s perform an ANOVA

```{r}
T_variance_analysis <- aov(mpg ~ ., data = mtcars)
summary(T_variance_analysis)
```

From the above Analysis of Variance, we can look for p-values of less than .5. This gives us cyl, disp, and wt to consider in addition to transmission type (am)
```{r}
T_multivar <- lm(mpg ~ cyl + disp + wt + am, data = mtcars)
summary(T_multivar)
```

This Multivariable Regression test now gives us an R-squared value of over .83, suggesting that 83% or more of variance can be explained by the multivariable model. P-values for cyl (number of cylinders) and weight are below 0.5, suggesting that these are confounding variables in the relation between car Transmission Type and Miles per Gallon.

## Residual Plot and Analysis
```{r}
par(mfrow = c(2, 2))
plot(T_multivar)
```

The “Residuals vs Fitted” plot here shows us that the residuals are homoscedastic. We can also see that they are normally distributed, with the exception of a few outliers.

